\entry{Course content}{This course is modular, divided into episodes that can last 1-4 weeks depending on topic complexity and class interest. There will be a quiz at the end of each episode. The following topics can be covered in class:
\smallskip

\begin{itemize}
	\item Intro: The scale of things. The Universe is HUGE. What does it mean to think like a scientist?
	\item Backyard astronomy: A tour of what you can observe and basic observation techniques. Become a proper amateur astronomer.
	\item Evolution of astronomy: from the Greek astronomers to the Heliocentric revolution of the Renaissance.
	\item Gravity: Orbits, Tides, and Rocket Science!
	\item Motion of the Earth: Time, Seasons and Eclipses.
	\item Anatomy of our Solar System: The Sun and the Planets.
	\item The nature of light, and how it can be used to study the Stars.
	\item To the stars, part I: The Star Detective. What can we learn from a dot of light?
	\item To the stars, part II: The evolution of stars, from birth to death, black holes, and the search of extrasolar planets.
	\item Galaxies: The Milky Way and beyond.
	\item Cosmology: From the Big Bang to the End of Time.
\end{itemize}
\smallskip

While there is no laboratory component in this course, experimental verifcation of physical reality is a key aspect of science and as such some class activities will occasionally involve experimental measurements and the analysis of data collected in the class or acquired from film clips. No lab reports will be required for this course. There is also the possibility of a field trip to the Planetarium, and an evening observation session with a telescope.
}