\entry{Course \mbox{competencies}}
{To exhibit an understanding of basic physics principles through analysis of phenomena in mechanics and geometric optics and to demonstrate preparedness for College level studies in Science.
\smallskip

Elements of the Competency:
\smallskip
\begin{enumerate}
	\item Knowledge
	\begin{itemize}
		\item To state the principles and laws of physics dealt with in this course.
		\item To state precise definitions of the physical quantities presented in this course, including proper SI units.
	\end{itemize}
	\item Problem-solving skills
	\begin{itemize}	
		\item To represent a physical situation by means of appropriate diagrams.
		\item To solve problems in an organized, methodical fashion, showing all work and explaining each step.
		\item To solve problems involving several main steps.
		\item To solve problems involving more than one principle or law.
		\item To display a certain facility in employing mathematical techniques to solve physics problems:
		\begin{itemize}	
			\item construction of appropriate mathematical representations of physical situations manipulation of vectors, both graphically and analytically, in two dimensions;
			\item set up and solution of algebraic equations and systems of equations;
			\item manipulation of trigonometric, logarithmic and exponential functions;
			\item construction and interpretation of graphs, including slopes, areas, intercepts and intersection points;
			\item competent use of a scientific calculator.
		\end{itemize}
	\end{itemize}
	\item Communication
	\begin{itemize}
		\item participate actively and articulately in class discussions and activities.
		\item To present answers to numerical problems in complete sentences.
		\item To explain simple phenomena from daily life, sports and technology:
		\begin{itemize}	
			\item in terms of the principles and laws presented in this course;
			\item in a few paragraphs;
			\item logically and coherently;
			\item in grammatical English.
		\end{itemize}
	\end{itemize}
\end{enumerate}}
\entry{\mbox{ }}{
\begin{enumerate}
\setcounter{enumi}{3}
	\item Laboratory Work
	\begin{itemize}
		\item To follow a detailed, written laboratory protocol with sufficient care to obtain reliable data.
		\item To work effectively as part of a lab group of two or three students.
		\item To present data in an organized way, using graphs and tables as appropriate.
		\item To analyze the data as directed in the lab protocol, and draw reasonable conclusions based on the results obtained.
		\item To submit a written laboratory report for each experiment in conformity with the course standards for lab reports, and on time.
	\end{itemize}
	\item Attitudes and behaviors
	\begin{itemize}
		\item To show curiosity about and interest in the study of physics and its applications.
		\item To have a serious and organized approach to college studies:
		\begin{itemize}	
			\item regular attendance;
			\item participation in class and labs;
			\item keeping up to date in courses, meeting deadlines for work;
			\item seeking help and advice as appropriate, to master material, to improve study skills and to plan academic career;
			\item setting priorities and managing time effectively;
			\item scrupulous academic honesty.
		\end{itemize}
	\end{itemize}
\end{enumerate}
}